Comparison among doublet predictions on benchmarking datasets

### 2024-07-22 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
use params to handle dataset names, and only run confusion matrices if there are two categories in the table

---
title: "Comparison among doublet predictions on benchmarking datasets"
author: Stephanie J. Spielman
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 4
    code_folding: hide
---

@@

```{r dataset names}
# find all dataset names to process:
dataset_names <- list.files(result_dir, pattern = "*_scrublet.tsv") |>
  stringr::str_remove("_scrublet.tsv")
```

@@

        confusion_result <- caret::confusionMatrix(
          # truth should be first
          table(
            "Truth" = df$ground_truth,
            "Consensus prediction" = df$consensus_call
          ),
          positive = "doublet"
        )

@@

        # Extract information we want to present later in a table
        tibble::tibble(
          "Dataset name" = dataset,
          "Kappa" = round(confusion_result$overall["Kappa"], 3),
          "Balanced accuracy" = round(confusion_result$byClass["Balanced Accuracy"], 3)
        )
    }
  ) |>
  dplyr::bind_rows()
```

>>>>

---
params: 
  datasets: "hm-6k pbmc-1B-dm pdx-MULTI HMEC-orig-MULTI"
title: "Comparison among doublet predictions on benchmarking datasets"
author: Stephanie J. Spielman
date: "`r Sys.Date()`"
output:
  html_notebook:
    toc: true
    toc_depth: 4
    code_folding: hide
---

@@

```{r dataset names}
# find all dataset names to process:
dataset_names <- stringr::str_split_1(params$datasets, pattern = " ")
```

@@

        # run confusion matrix only if there are both singlets and doublets
        if (length(unique(df$consensus_call)) == 2) {
            confusion_result <- caret::confusionMatrix(
            # truth should be first
            table(
              "Truth" = df$ground_truth,
              "Consensus prediction" = df$consensus_call
            ),
            positive = "doublet"
          )

@@

          # Extract information we want to present later in a table
          return(
            tibble::tibble(
              "Dataset name" = dataset,
              "Kappa" = round(confusion_result$overall["Kappa"], 3),
              "Balanced accuracy" = round(confusion_result$byClass["Balanced Accuracy"], 3)
            ) 
          )
        }
    }
  ) |>
  dplyr::bind_rows()
```
